[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-17 analysis/paper.Rmd
Adds references to the original tables and images into paper.rmd

>>>>

```{r, table1, fig.cap="Table 1 from the original paper", echo=FALSE}
knitr::include_graphics("original_paper_table_1.png")
```

The results from Table 1 in the original paper are shown in Figure \@ref(fig:table1).

```{r, table2, fig.cap="Table 2 from the original paper", echo=FALSE}
knitr::include_graphics("original_paper_table_2.png")
```

The results from Table 2 in the original paper are shown in Figure \@ref(fig:table2).
